The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-11 paper.tex
now final draft?

Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

@@

In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
purposes we will assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
Tikhonov-regularized spherical harmonic coefficients is
\begin{equation}
    \b C = n \b V (\b\Sigma^2 + \varepsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
\end{equation}
Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \varepsilon)^2$.  In the
absence of Tikhonov regularization ($\varepsilon=0$) singular components with the smallest singular
values -- the ones that the interferometer is the least sensitive to -- actually come to dominate
the covariance of the measured spherical harmonic coefficients. Tikhonov regularization improves
this situation by downweighting these components.

@@

In practice, the L-curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
However better results can often be obtained by tuning the value of $\varepsilon$. For instance
increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution in the map by
up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in traditional
imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.  For the
OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
Table~\ref{tab:summary}.

@@

The PSF of a dirty $m$-mode analysis map may be computed with
\begin{equation}\label{eq:psf}
    \b a_\text{PSF}(\theta, \phi)
        = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
\end{equation}
where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
the PSF at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta, \phi)$ is the
vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given by
\begin{equation}
    \b a_\text{PS}(\theta, \phi) = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, \phi) \\
        \vdots \\
    \end{pmatrix}
    = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, 0)\times e^{im\phi} \\
        \vdots \\
    \end{pmatrix} \,.
\end{equation}
In general the PSF can be a function of the right ascension and declination. However point sources
at the same declination take the same track through the sky and therefore (barring any ionospheric
effects) will have the same PSF. The PSF is therefore only a function of the declination. For
example, sources at low elevations will tend to have an extended PSF along the north-south axis due
to baseline foreshortening. For the OVRO-LWA antenna configuration
(Figure~\ref{fig:antenna-layout}), example PSFs at three separate frequencies are shown in
Figure~\ref{fig:psf}.  Adapting CLEAN for $m$-mode analysis requires either pre-computing
Equation~\ref{eq:psf} at a grid of declinations, or a method for rapidly evaluating
Equation~\ref{eq:psf} on the fly.

%\citep{2011MNRAS.413..411B} % I think Lincoln wants me to cite this paper

@@

%\todo{describe blurring to avoid cleaning the diffuse emission}

@@

Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
is when these sources are at high elevations.  The antenna complex gains are measured from a 22
minute track of data when Cyg~A and Cas are at high elevations. The gains measured in this way are
then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of Cyg~A
and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while the flux
of Cas~A is measured from the data itself (using a preliminary calibration solved for with a
fiducial Cas~A spectrum).

@@

We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
Per~B\footnote{
    At 74~MHz, Per~B is about two times brighter than Per~A.
}, and
3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
model at several frequencies. This process is repeated for each frequency channel. Residuals for
Cyg~A and Cas~A can be seen in Figure~\ref{fig:scintillation}.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have measured flux variations of 50\% between adjacent 13 second integrations.  The variance at
36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
origin. The measured position offset of each source is a measurement of the ionospheric phase
gradient across the array.  This varies on slower 10 minute timescales refracting each source by as
much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the ionosphere
pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe $\sim
1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on similar
$\sim10$ minute timescales.  The impact of these effects on the sky maps is simulated in
\S\ref{sec:ionosphere}.

@@

The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg~A during gain
calibration. However gain calibration is also a function of the beam model and the spectrum used for
Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival date from the
literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
low-frequency radio sources with calibrated flux measurements from one (just Cyg~A) to eleven in
total. While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is
somewhat more limited because the lowest frequency observations come from the VLA 4-band system. As
a consequence the PB17 flux scale is not valid below 50 MHz.

@@

Eight sky maps were constructed using Tikhonov-regularized $m$-mode analysis imaging and cleaning
with observations from the OVRO-LWA. Each map is individually shown in
Figure~\ref{fig:channel-maps}, and Figure~\ref{fig:three-color} is a three-color image constructed
from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz. The maps cover the sky north of
$\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The 8 brightest northern
hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, Per~B,
and 3C~353) as described in \S\ref{sec:source-removal}, and there is a small blank region near
$l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the observing
window. The properties of each map, including frequency, bandwidth, angular resolution, and thermal
noise are presented in Table~\ref{tab:summary}.

@@

The noise in each map is empirically measured using jackknife resampling. The dataset is split into
even- and odd-numbered integrations. These two groups are imaged and cleaned independently, before
being compared against the maps constructed from all of the available data using the standard
jackknife variance estimator. This estimate of the variance includes all sources of error that
operate on $\sim13$ second timescales (the integration time) such as thermal noise and rapid
ionospheric fluctuations, but does not account for more slowly varying effects (for example,
sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.

In the absence of a zero-level correction, a pixel-by-pixel power law fit to the new maps is
impossible. In general this zero-level correction requires calibrated total power measurements that
will be included in future work.  Instead, temperature-temperature plots (T-T plot) can be used to
measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
This method relies on the assumption that all pixels in a given region are described by the same
power law. In that case there exists a linear relationship between the brightness temperature at
frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
spectral index between the two frequencies. T-T plots can fail to obtain a reliable measure of the
spectral index in two ways.  First, if there is not enough dynamic range in the emission region
there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free) then
a single power-law interpretation of the emission in that region will be poor. Consequently spectral
indices estimated from T-T plots can require careful interpretation.

In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated in each part of
the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
73.152~MHz. Contours of constant $R^2$ (the coefficient-of-determination) are overlaid. If $R^2\sim
1$, the spectral index is reliable because there is locally a strong linear correlation between
36.528~MHz and 73.152~MHz. However if $R^2\ll 1$, the spectral index calculation is unreliable.
$R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
strong correlation between the two frequencies. $R^2$ also tends to drop in the vicinity of
\ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
assumption of a single spectral index. Therefore we should restrict our interpretation of
Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
can be seen with higher resolution in Figure~\ref{fig:three-color}. Along the galactic plane,
especially towards the galactic center, \ion{H}{2} regions appear as blue shadows due to free-free
absorption.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/lwa1/lwa1}
    \caption{\todo{a thing}}
    \label{fig:lwa1-comparison}
\end{figure*}

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced 9 maps of the sky
between 35~MHz and 80~MHz. 6 of these maps are interior to the frequency range spanned by this work.
A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In this
figure the LLFSS maps are filtered to remove the monopole and all modes with $m=0$, and the OVRO-LWA
maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
LWA1 map. The dominant feature in this map is a shift of the galactic plane. This feature is also
seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
\citet{2017MNRAS.469.4537D}). Therefore we conclude that this is an artifact of the LLFSS. Otherwise
at 60~MHz the agreement is generally better than 10\%. However at lower frequencies the agreement
deterioriates to about 20\%.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=0.32\textheight]{figures/guzman/guzman}
    \caption{
        This Mollweide projection map compares the fractional difference between the Guzm\'{a}n 45
        MHz map, and the OVRO-LWA map at 46.992 MHz (degraded to $5^\circ$ resolution). A positive
        value indicates regions where the OVRO-LWA map has more emission that the Guzm\'{a}n map,
        and a negative value indicates regions where the Guzm\'{a}n map has more emission than the
        OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
        subtracted from the OVRO-LWA maps but not the Guzm\'{a}n map.
    }
    \label{fig:guzman-comparison}
\end{figure*}

The Guzm\'{a}n 45 MHz map \citep{2011A&A...525A.138G} is compiled from a southern hemisphere survey
\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
small gap around the NCP. In this work the zero-level is set by comparing against published
low-frequency measurements in the literature in six different directions.

@@

One of the key assumptions made by $m$-mode analysis is that the sky is static.  We assume that the
only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
fringe patterns of the interferometer. At low frequencies the ionosphere violates this assumption.
In particular, ionospheric scintillation and refractive offsets will cause even static sources to
exhibit significant variability (Figure~\ref{fig:scintillation}).

@@

The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
arising from ionospheric fluctuations. The effect of this can be seen in
Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
source is always located exactly at the location of Cas A. In the middle panel, the source is
allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
the point source is effectively unchanged from the ideal PSF. In the right panel, the source
position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
Figure~\ref{fig:3C134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
vicinity of bright point sources.

@@

In the first case, all sources at a given declination take the same path through the antenna primary
beam. If the antenna response is overestimated along this track then all sources at this declination
will have their flux underestimated. Similarly if the antenna response is underestimated then all
the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
show a clear pattern with declination. Two sources have a clear systematic offset at all
frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
declination to Lyn A, which appears, if anything, to have its flux overestimated. The absence of a
coherent pattern does not eliminate the possibility of beam errors effecting the flux scale, but it
does mean that these errors are at least comparable to the errors inherent to the flux scale itself.

>>>>

Current 21~cm cosmology experiments can be broadly separated into two classes: global signal
experiments that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm
transition after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global signal experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

@@

In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
purposes we will assume that $\b N=n\b I$ for some $n>0$. In this case the covariance of the
Tikhonov-regularized spherical harmonic coefficients is
\begin{equation}
    \b C = n \b V (\b\Sigma^2 + \varepsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
\end{equation}
Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \varepsilon)^2$.  In the
absence of Tikhonov regularization ($\varepsilon=0$) singular components with the smallest singular
values -- the ones that the interferometer is the least sensitive to -- actually come to dominate
the covariance of the measured spherical harmonic coefficients. Tikhonov regularization improves
this situation by downweighting these components.

@@

In practice, the L-curve should be used as a guide to estimate a reasonable value of $\varepsilon$.
However better results can often be obtained by tuning the value of $\varepsilon$. For instance
increasing the value of $\varepsilon$ can improve the noise properties of the map by down-weighting
noisy modes. Decreasing the value of $\varepsilon$ can improve the resolution of the map by
up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
choosing the value of $\varepsilon$ is analagous to picking the weighting scheme in traditional
imaging where robust weighting schemes can be tuned to similar effect \citep{briggs}.  For the
OVRO-LWA we selected $\varepsilon = 0.01$ across all frequency channels. The distribution of
singular values of the transfer matrix with respect to $\sqrt{\varepsilon}$ is summarized in
Table~\ref{tab:summary}.

@@

The PSF of a dirty $m$-mode analysis map may be computed with
\begin{equation}\label{eq:psf}
    \b a_\text{PSF}(\theta, \phi)
        = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
\end{equation}
where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
the PSF at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta, \phi)$ is the
vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given by
\begin{equation}
    \b a_\text{PS}(\theta, \phi) = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, \phi) \\
        \vdots \\
    \end{pmatrix}
    = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, 0)\times e^{im\phi} \\
        \vdots \\
    \end{pmatrix} \,.
\end{equation}
In general the PSF can be a function of the right ascension and declination. However point sources
at the same declination take the same track through the sky and (barring any ionospheric effects)
will have the same PSF. The PSF is therefore only a function of the declination. For example,
sources at low elevations will tend to have an extended PSF along the north-south axis due to
baseline foreshortening. For the OVRO-LWA antenna configuration (Figure~\ref{fig:antenna-layout}),
example PSFs at three separate frequencies are shown in Figure~\ref{fig:psf}.  Adapting CLEAN for
$m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of declinations, or
a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.

@@

@@

Cyg~A and Cas~A are -- by an order of magnitude -- the brightest point-like radio sources in the
northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
is when these sources are at high elevations.  The antenna complex gains are measured from a 22
minute track of data when Cyg~A and Cas~A are at high elevations. The gains measured in this way are
then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of Cyg~A
and Cas~A. The model flux of Cyg~A is set to the \citet{1977A&A....61...99B} spectrum while the flux
of Cas~A is measured from the data itself (using a preliminary calibration solved for with a
fiducial Cas~A spectrum).

@@

We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
Per~B\footnote{
    At 74~MHz, Per~B is about two times brighter than Per~A.
}, and
3C~353) as they pass through the sky, and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
model at several frequencies. This process is repeated for each frequency channel. Residuals for
Cyg~A and Cas~A can be seen in Figure~\ref{fig:scintillation}.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have measured flux variations of 50\% between adjacent 13 second integrations.  The variance at
36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
origin. The measured position offset of each source is a measurement of the ionospheric phase
gradient across the array.  This varies on slower 10 minute timescales, with each source refracting
by as much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the
ionosphere pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe
$\sim 1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on
similar $\sim10$ minute timescales, which is consistent with what is seen here.  The impact of these
effects on the sky maps is simulated in \S\ref{sec:ionosphere}.

@@

The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg~A during gain
calibration. However gain calibration is also a function of the beam model and the spectrum used for
Cas~A. Recent work by \citet{2012MNRAS.423L..30S} (hereafter SH12) using archival data from the
literature and \citet{2017ApJS..230....7P} (hereafter PB17) using the VLA has expanded the number of
low-frequency radio sources with calibrated flux measurements from one (just Cyg~A) to eleven in
total. While the SH12 flux scale is valid between 30 MHz and 300 MHz, the PB17 flux scale is
somewhat more limited because the lowest frequency observations come from the VLA 4-band system. As
a consequence the PB17 flux scale is not valid below 50 MHz.

@@

Eight sky maps were constructed using Tikhonov-regularized $m$-mode analysis imaging and cleaning
with observations from the OVRO-LWA. Each map is individually shown in
Figure~\ref{fig:channel-maps}, and Figure~\ref{fig:three-color} is a three-color image constructed
from the maps at 36.528~MHz, 52.224~MHz, and 73.152~MHz. The maps cover the sky north of
$\delta=-30^\circ$ with $\sim 15$ arcmin angular resolution resolution. The 8 brightest northern
hemisphere point sources are removed from each map (Cyg~A, Cas~A, Vir~A, Tau~A, Her~A, Hya~A, Per~B,
and 3C~353) as described in \S\ref{sec:source-removal}, and there is a small blank region near
$l=+45.7^\circ$, $b=-47.9^\circ$ corresponding to the position of the Sun during the observing
window. The properties of each map -- including frequency, bandwidth, angular resolution, and
thermal noise -- are presented in Table~\ref{tab:summary}.

@@

The noise in each map is empirically measured using jackknife resampling. The dataset is split into
even- and odd-numbered integrations. These two groups are imaged and CLEANed independently, before
being compared against the maps constructed from all of the available data using the standard
jackknife variance estimator. This estimate of the variance includes all sources of error that
operate on $\sim13$ second timescales (the integration time) such as thermal noise and rapid
ionospheric fluctuations, but does not account for more slowly varying effects (for example,
sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.

In the absence of a zero-level correction, a pixel-by-pixel power law fit to the new maps is
impossible. In general this zero-level correction requires calibrated total power measurements that
will be included in future work.  Instead, temperature-temperature plots (T-T plots) can be used to
measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
This method relies on the assumption that all pixels in a given region are described by the same
power law. In that case there exists a linear relationship between the brightness temperature at
frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
spectral index between the two frequencies. T-T plots can fail to obtain a reliable measure of the
spectral index in two ways.  First, if there is not enough dynamic range in the emission region
there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free) then
a single power-law interpretation of the emission in that region will be poor. Consequently spectral
indices estimated from T-T plots can require careful interpretation.

In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated in each part of
the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
73.152~MHz. Contours of constant $R^2$ (the coefficient-of-determination) are overlaid. If $R^2\sim
1$, the spectral index is reliable because there is locally a strong linear correlation between
36.528~MHz and 73.152~MHz. However if $R^2\ll 1$, the spectral index calculation is unreliable.
$R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
strong correlation between the two frequencies. $R^2$ also tends to drop in the vicinity of
\ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
assumption of a single spectral index. Therefore we should restrict our interpretation of
Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
can be seen with higher resolution in Figure~\ref{fig:three-color}. In this figure \ion{H}{2}
regions appear as blue shadows along the galactic plane due to the increasing impact of free-free
absorption at lower frequencies.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/lwa1/lwa1}
    \caption{
        The fractional difference between maps from the LWA1 Low Frequency Sky Survey and the
        OVRO-LWA maps (Figure~\ref{fig:channel-maps}) after interpolating to the corresponding
        frequency and smoothing to the corresponding resolution. A positive value indicates regions
        where the OVRO-LWA map has more emission that the corresponding LWA1 Low Frequency Sky
        Survey map. Cas A, Cyg A, Vir A, and Tau A are masked due to the fact that they are
        subtracted from the OVRO-LWA maps.
    }
    \label{fig:lwa1-comparison}
\end{figure*}

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced 9 maps of the sky
between 35~MHz and 80~MHz. 6 of these maps are interior to the frequency range spanned by this work.
A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In this
figure the LLFSS maps are filtered to remove the monopole and all modes with $m=0$, and the OVRO-LWA
maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
LLFSS map. The dominant feature in this map is a shift of the galactic plane. This feature is also
seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
\citet{2017MNRAS.469.4537D}). Therefore we conclude that this is an artifact of the LLFSS. Otherwise
at 60~MHz the agreement is generally better than 10\%. However at lower frequencies the agreement
deterioriates to about 20\%.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=0.32\textheight]{figures/guzman/guzman}
    \caption{
        This Mollweide projected map compares the fractional difference between the Guzm\'{a}n 45
        MHz map, and the OVRO-LWA maps (Figure~\ref{fig:channel-maps}) interpolated to 45~MHz
        (degraded to $5^\circ$ resolution). A positive value indicates regions where the OVRO-LWA
        map has more emission that the Guzm\'{a}n map, and a negative value indicates regions where
        the Guzm\'{a}n map has more emission than the OVRO-LWA map. Cas A, Cyg A, Vir A, and Tau A
        are masked due to the fact that they are subtracted from the OVRO-LWA maps but not the
        Guzm\'{a}n map.
    }
    \label{fig:guzman-comparison}
\end{figure*}

The Guzm\'{a}n 45 MHz map \citep{2011A&A...525A.138G} is compiled from a southern hemisphere survey
\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
small gap around the NCP. In this work the zero-level is set by comparing against published
low-frequency measurements in six different directions.

@@

One of the key assumptions made by $m$-mode analysis is that the sky is static.  We assume that the
only time-dependent behavior is the rotation of the Earth, which slowly rotates the sky through the
fringe pattern of the interferometer. At low frequencies the ionosphere violates this assumption.
In particular, ionospheric scintillation and refractive offsets will cause even static sources to
exhibit significant variability (Figure~\ref{fig:scintillation}).

@@

The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
arising from ionospheric fluctuations. The effect of this can be seen in
Figure~\ref{fig:ionospheric-simulations}. In this simulation a point source is placed at the
location of Cas~A. In one case the source is allowed to scintillate in the same way Cas~A does in
Figure~\ref{fig:scintillation}, but the source is always located exactly at the location of Cas~A.
In the second case the source position is allowed to vary in the same way Cas~A does in
Figure~\ref{fig:scintillation}, but the flux of the source exactly traces the beam model. The
scintillation, although large, introduces only $<0.3\%$ errors in the vicinity of bright point
sources. Refractive offsets, however, can introduce $\sim 15\%$ errors at 36.528~MHz and $\sim 5\%$
errors at 73.152~MHz.  Because the sidelobes of the PSF are altered from that of the ideal PSF,
refractive offsets will restrict the dynamic range it is possible to obtain with the CLEAN algorithm
described in \S\ref{sec:clean}. This effect can be clearly seen in Figure~\ref{fig:3C134}, where
10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As expected for an ionospheric
effect these errors decrease to a few percent at 52.224~MHz, and less at 73.152~MHz. We therefore
conclude that ionospheric effects directly limit the dynamic range in the vicinity of bright point
sources.

@@

In the first case, all sources at a given declination take the same path through the antenna primary
beam. If the antenna response is overestimated along this track then all sources at this declination
will have their flux underestimated. Similarly if the antenna response is underestimated then all
the sources will have their flux overestimated. The errors in Figure~\ref{fig:flux-scale} do not
show a clear pattern with declination. Two sources have a clear systematic offset at all
frequencies: 3C 353 and 3C 380. 3C 353 is the second southernmost source, but Hya A -- the first
southernmost source -- does not exhibit this systematic error. Similarly 3C 380 is at a comparable
declination to Lyn A, which appears, if anything, to have its flux systematically offset in the
other direction. The absence of a coherent pattern does not eliminate the possibility of beam errors
effecting the flux scale, but it does mean that these errors are at least comparable to the errors
inherent to the flux scale itself.
